---
title: "ABIS-psoriasis excluding auto-immune diseases confounders for multivariable regression model"
author: "Debojyoti Das"
date: "2023-09-19"
output: html_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
curr_os <- Sys.info()["sysname"][[1]]

output_dir <- "C:\\Users\\debda22\\OneDrive - Linköpings universitet\\early_nutrition\\without_auto_immune_disease\\confounders"

dir.create(output_dir)
```

```{r}
pacman::p_load(
  haven,        # File import
  here,         # File locator
  sjlabelled,
  janitor,      # 
  data.table,   #
  flextable,    #
  comprehenr,   # List comprehension in R
  tidyverse,    # data management + ggplot2 graphics, 
  stringr,      # manipulate text strings 
  purrr,        # loop over objects in a tidy way
  gtsummary,    # summary statistics and tests 
  broom,        # tidy up results from regressions
  lmtest,       # likelihood-ratio tests
  parameters,   # alternative to tidy up results from regressions
  see,          # alternative to visualize forest plots
  easystats,    # Forest plot
  kableExtra,
  forestplot,
  rempsyc,
  ggpubr,
  lattice,
  naniar,
  VIM,
  mice,          # multivariate
  howManyImputations,
  CALIBERrfimpute,
  miceRanger,
  parallel,
  parameters,
  glmglrt,
  MASS
  )
```

load helping functions

```{r, include=FALSE}
# helper functions for imputation
source("C:/Users/debda22/OneDrive - Linköpings universitet/Rmd_and_R_files/Functions_rmph.R")
source("C:/Users/debda22/OneDrive - Linköpings universitet/Rmd_and_R_files/helper_functions.R")
source("C:/Users/debda22/OneDrive - Linköpings universitet/Rmd_and_R_files/early_nutrition/all_parameters_ABIS_year_1.R")
```

Read cohort data from SAV format file

```{r}
if (curr_os == "Windows"){
  abis_table <- read_sav("C:\\Users\\debda22\\OneDrive - Linköpings universitet\\Linkoping_projects\\ABIS_RAW_DATA_SPSS\\ABIS_data_base.sav")
  psoriasis_diagonistic_table <- read_sav("C:\\Users\\debda22\\OneDrive - Linköpings universitet\\Linkoping_projects\\ABIS_RAW_DATA_SPSS\\L40_corrected.sav")
  } else {
  abis_table <- read_sav("/Users/debojyoti/OneDrive - Linköpings universitet/Linkoping_projects/ABIS_RAW_DATA_SPSS/ABIS_data_base.sav")
  psoriasis_diagonistic_table <- read_sav("/Users/debojyoti/OneDrive - Linköpings universitet/Linkoping_projects/ABIS_RAW_DATA_SPSS/L40_corrected.sav")
  }

severity <- readxl::read_excel("C://Users/debda22/OneDrive - Linköpings universitet/Linkoping_projects/ABIS_RAW_DATA_SPSS/Psoriasis  severity.xlsx")
```


```{r}
severity <- severity %>%
  mutate(
    severity = case_when(
      grepl("sever",`Mild form`,ignore.case = TRUE) ~ "severe",
      grepl("mild",`Mild form`,ignore.case = TRUE) ~ "mild",
      TRUE ~ NA
      )
  ) %>% dplyr::select(ABISnr, severity)      

severe_psoriasis_abis <- (severity %>% filter(severity == "severe"))$ABISnr
mild_psoriasis_abis <- (severity %>% filter(severity == "mild"))$ABISnr
```


```{r}
abis_table <- abis_table[,c("ABISnr",
                            "barn_år_mån", 
                            "b_5",
                            "b_6",
                            "b_7a",
                            # "b_7b", # 85.70 % missing hence excluded
                            "b_8",
                            "b_9",
                            "b_10",
                            "b_45",
                            "b_46",
                            "b_49",
                            "b_53",
                            "b_54",
                            "b_55",
                            "b_56",
                            "b_57",
                            "b_58",
                            "b_59",
                            "b_60",
                            "b_61",
                            "b_62",
                            "b_65", # chocolate
                            "b_66", # sweet                            
                            "e_34p_1", 
                            "e_34p_2",
                            "e_34p_3",
                            "f_28o_1",
                            "f_28o_2",
                            "f_28o_3",
                            "gv_21o1",
                            "gv_21o2",
                            "gv_21o3",
                            "fr_12",
                            "fr_27",
                            "fr_28",
                            "Gender")]

abis_table <- abis_table %>% 
  mutate(
    child_dob = as.Date(as.yearmon(as.character(barn_år_mån), format = "%Y%m"))
    )

abis_table.labels <- to_vec(for (col in names(abis_table)) 
  if(is.null(attr(abis_table[[col]], "label"))) col 
  else attr(abis_table[[col]], "label"))

psoriasis_diagonistic_table.labels <- 
  to_vec(for (col in names(psoriasis_diagonistic_table)) 
    if(is.null(attr(psoriasis_diagonistic_table[[col]], "label"))) col 
    else attr(psoriasis_diagonistic_table[[col]], "label"))

abis_table_labels <- 
  data.frame("Name" = names(abis_table), "Label" = abis_table.labels)
psoriasis_diagonistic_labels <- 
  data.frame("Name" = names(psoriasis_diagonistic_table), 
             "Label" = psoriasis_diagonistic_table.labels)

```

Merge the data to include psoriasis diagonistics

```{r}
psoriasis_data_full <- left_join(abis_table, 
                             psoriasis_diagonistic_table,
                             by = "ABISnr") %>% 
  mutate(Diagnos = replace(Diagnos, is.na(Diagnos), "")) %>%
  # reformat the date (of detection)
  mutate(
    first_detection = as.Date(as.character(övFörsta), format = "%Y%m%d"), 
    second_detection = as.Date(as.character(övSenaste), format = "%Y%m%d")
    ) %>%
  mutate(
    age_first_detection = lubridate::time_length(
      difftime(first_detection,child_dob), "years"),
    age_second_detection = lubridate::time_length(
      difftime(second_detection,child_dob), "years"),
    # detection_date_diff = lubridate::time_length(
    #   difftime(second_detection,first_detection), "days")
  ) %>% mutate_if(is.numeric, round,2)

```

Remove attributes

```{r}

for (col in names(psoriasis_data_full)) {
  if(!(is.null(attr(psoriasis_data_full[[col]], "label")))){
    attr(psoriasis_data_full[[col]], "label") <- NULL
  }
  if(!(is.null(attr(psoriasis_data_full[[col]], "labels")))){
    attr(psoriasis_data_full[[col]], "labels") <- NULL
  }
  if(!(is.null(attr(psoriasis_data_full[[col]], "format.spss")))){
    attr(psoriasis_data_full[[col]], "format.spss") <- NULL
  }  
  if(!(is.null(attr(psoriasis_data_full[[col]], "names")))){
    attr(psoriasis_data_full[[col]], "names") <- NULL
  } 
  if(!(is.null(attr(psoriasis_data_full[[col]], "display_width")))){
    attr(psoriasis_data_full[[col]], "display_width") <- NULL
  }   
}

attr(psoriasis_data_full, "notes") <- NULL


for (col in names(psoriasis_data_full)) {
  if(is.labelled(psoriasis_data_full[[col]])){
    
    psoriasis_data_full[col] <- unlabel(psoriasis_data_full[[col]])
    
  }
  
}


psoriasis_data_full <- as.data.frame(psoriasis_data_full)

```

```{r}
psoriasis_data_full <- psoriasis_data_full %>%
  mutate(
    composite_psoriasis_heredity = pmin(
      e_34p_1,
      e_34p_2,
      e_34p_3,
      f_28o_1,
      f_28o_2,
      f_28o_3,
      gv_21o1,
      gv_21o2,
      gv_21o3, 
      na.rm = TRUE)
    ) %>% 
  mutate(
    first_degree_psoriasis_heredity = ifelse(
      is.na(composite_psoriasis_heredity),0,1)
  ) %>% 
  dplyr::select(-c(composite_psoriasis_heredity,
            child_dob,barn_år_mån,
            e_34p_1,e_34p_2,e_34p_3,
            f_28o_1,f_28o_2,f_28o_3,
            gv_21o1,gv_21o2,gv_21o3,
            övAntal,övFörsta,övSenaste,
            first_detection,second_detection
            )
         )
```

convert dichotomous variables to 0/1

```{r}
psoriasis_data_full <- psoriasis_data_full %>%  
  mutate(across(                                      
    .cols = all_of(c("Diagnos")),  ## for each column listed and "outcome"
    .fns = ~case_when(                              
      . %in% c("L40")   ~ 1,  ## recode L40 (psoriasis diagnosis) to 1
      . %in% c("") ~ 0,       ## not present  to 0
      TRUE ~ NA_real_)        ## otherwise set to missing
    )
  ) 
  
```

remove cases with other auto immune diseases other than psoriasis

```{r}
print("number of participants with other autoimmune diseases")
print(
  nrow(
    psoriasis_data_full[
      which((
        (psoriasis_data_full$AutoimmDisease == 1)&
          (psoriasis_data_full$Diagnos != 1))),]))

print("number of participants before filtering")
print(nrow(psoriasis_data_full))

print("number of first order heredity psoriasis cases before filtering")
print(psoriasis_data_full %>% 
        filter(first_degree_psoriasis_heredity == 1) %>%
        nrow()
      )

psoriasis_data_full <- psoriasis_data_full %>% 
  filter(!((AutoimmDisease == 1)&(Diagnos != 1)))

# remove rows with missing sex information
psoriasis_data_full <- psoriasis_data_full %>% filter(!is.na(Gender))

print("number of participants after filtering")
print(nrow(psoriasis_data_full))

print("number of first order heredity psoriasis cases after filtering")
print(psoriasis_data_full %>% 
        filter(first_degree_psoriasis_heredity == 1) %>%
        nrow()
      )
```

subset data to include only variables of interest and outcome

```{r}
puberty_age <- 13

lower_age_puberty <- "psoriasis before age 13"
upper_age_puberty <- "psoriasis after age 13"

psoriasis_detection_age_data <- psoriasis_data_full[,c("ABISnr",
                                         "age_first_detection",
                                         "age_second_detection")] %>% 
  mutate(age_first_detection_cat = case_when(
    age_first_detection < puberty_age ~ lower_age_puberty,
    age_first_detection >= puberty_age ~ upper_age_puberty, 
    TRUE ~ "Not detected")
    )

```

```{r}
explanatory_vars <- names(psoriasis_data_full)[
  !(names(psoriasis_data_full) %in% 
      c("ABISnr", "Diagnos", 
        "age_first_detection",
        "age_second_detection",
        "AutoimmDisease")
    )
  ]
psoriasis_data_full <- psoriasis_data_full[,c("ABISnr", 
                                              explanatory_vars,
                                              "Diagnos")]


```

custom create variable fish intake from any source and add to list of variables of interest

```{r}
psoriasis_data_full <- psoriasis_data_full %>% 
  mutate(fish = pmin(b_56,b_57,b_58, na.rm = TRUE))
explanatory_vars <- c(explanatory_vars, "fish")
```

```{r}
categorical_explanatory_vars <- names(
  psoriasis_data_full)[!(names(psoriasis_data_full) %in% 
                           c("ABISnr",
                             "fr_12",
                             "first_degree_psoriasis_heredity",
                             "fish", 
                             "Diagnos"))]

```

variable value label correspondence data frame

```{r}
explanatory_vars_df <- data.frame(
  v = character(), 
  v_labels = character(),
  labels = character()
  )


for (col in categorical_explanatory_vars){
  curr_label <- attr(abis_table[[col]], "labels")
  
  v <-list(col)
  if(!is.null(curr_label)){  
    v_labels <- list(attr(abis_table[[col]], "labels"))
    curr_dt <- data.frame(I(v[[1]]), I(v_labels[[1]]))
    curr_dt[["labels"]] <- rownames(curr_dt)
  } else {
    v_labels <- levels(factor(abis_table[[col]]))
    curr_dt <- data.frame(I(v[[1]]), I(v_labels))
    curr_dt[["labels"]] <- paste0(v_labels," ")
  }
  colnames(curr_dt) <- c("variable", "value", "label")
  
  explanatory_vars_df <- rbind(explanatory_vars_df,curr_dt)
}

rownames(explanatory_vars_df) <- seq(1,dim(explanatory_vars_df)[1])
colnames(explanatory_vars_df) <- c("variable", "value", "label")

```

```{r}
explanatory_vars_df <- explanatory_vars_df %>% 
  rbind(list(variable = rep("fish",4), value = seq(1,4), 
             label = c("daily","3-5 times/week","1-2 times/week", "seldom")
             )
        )
categorical_explanatory_vars <- c(categorical_explanatory_vars, "fish")
```

answer not given

```{r}
ambiguous_answer <- explanatory_vars_df[((explanatory_vars_df$label %in% c(
              "do not know",
              "Do not know",
              "don't know", 
              "dont know", 
              "don`t know"))),]

for (v in ambiguous_answer$variable) {
  value2replace <- ambiguous_answer[ambiguous_answer$variable == v,]$value
  psoriasis_data_full[[v]][which(psoriasis_data_full[[v]] == value2replace)] <- NA
}
```

```{r}
explanatory_vars_df <- explanatory_vars_df[
  (!(explanatory_vars_df$label %in% c(
    "do not know",
    "Do not know",
    "don't know",
    "dont know",
    "don`t know"))),]

expected_values_df <- explanatory_vars_df %>% 
  group_by(variable) %>%
  summarise(min_val = min(value),max_val = max(value))
```

save original data with missing values factorize variables that are to be treated as categorical before imputation is carried out

```{r}
unfactored_original_psoriasis_data_full <- psoriasis_data_full

for (cv in unlist(all_parameters$category_variable)){
  
  curr_parameters <- all_parameters[all_parameters$category_variable == cv,]
  
  psoriasis_data_full <- categorise_variable(psoriasis_data_full,
                          variable2categorise = curr_parameters$variable2categorise[[1]],
                          category_variable = curr_parameters$category_variable[[1]],
                          breaks = curr_parameters$breaks[[1]],
                          labels = curr_parameters$labels[[1]]
)
}

psoriasis_data_full[["first_degree_psoriasis_heredity"]] <- 
  factor(psoriasis_data_full[["first_degree_psoriasis_heredity"]])
psoriasis_data_full[["Diagnos"]] <- factor(psoriasis_data_full[["Diagnos"]])
```

remove variables that have been recoded to categorical variables

```{r}
psoriasis_data_full <- psoriasis_data_full %>%
  dplyr::select(-categorical_explanatory_vars)
# rename gestational variable
psoriasis_data_full["gestational_age"] <- psoriasis_data_full$fr_12
psoriasis_data_full$fr_12 <- NULL

# print(as.formula(paste("Diagnos ~ ", paste(names(psoriasis_data_full)[c(4:32,2)], collapse = "+"))))
```

re-oreder some of the levels

```{r}
for (voi in names(psoriasis_data_full)[c(4:11,16:21,24:25)]) {
   old_levels = levels(psoriasis_data_full[[voi]])
   psoriasis_data_full[[voi]] <- factor(psoriasis_data_full[[voi]],
       levels = rev(old_levels)
   ) 
}
```

counts table
```{r}
gestational_age_diagnos <- unlist(
  (
    (
      psoriasis_data_full %>% 
        tabyl(gestational_age, Diagnos))[,c(2,3)] %>% 
      colSums()
    )
  )
confounder_table <- data.frame(
  feature = "gestational_age",
  healthy = gestational_age_diagnos[[1]],
  psoriasis = gestational_age_diagnos[[2]]
)  %>% 
  mutate(
    healthy_pct = paste(healthy, " (",round(100*(healthy/sum(healthy + psoriasis)),2),"%)", sep = ""),
    psoriasis_pct = paste(psoriasis, " (",round(100*(psoriasis/sum(healthy + psoriasis)),2),"%)", sep = "")
    )

confounders <- names(psoriasis_data_full)[c(2,26:28)]

for (i in seq_along(confounders)) {
  
  confounder_table <- rbind(confounder_table,
                            data.frame(
                                feature = confounders[[i]],
                                healthy = c(NA),
                                psoriasis = c(NA),
                                healthy_pct = c(NA),
                                psoriasis_pct = c(NA)
                                )
                            )
  counts_table <- psoriasis_data_full %>% tabyl(!!sym(confounders[[i]]),Diagnos)
  names(counts_table) <- c("feature", "healthy", "psoriasis")
  
  counts_table <- counts_table %>%
    mutate(
      healthy_pct = paste(healthy, " (",round(100*(healthy/sum(healthy + psoriasis)),2),"%)", sep = ""),
      psoriasis_pct = paste(psoriasis, " (",round(100*(psoriasis/sum(healthy + psoriasis)),2),"%)", sep = "")
    )
  
  confounder_table <- rbind(confounder_table,counts_table)
}

confounder_table <- confounder_table %>% 
  mutate(feature = if_else((feature=="0"),"no",feature)) %>% 
  mutate(feature = if_else((feature=="1"),"yes",feature)) %>% 
  mutate(feature = if_else(is.na(feature),"missing",feature)) %>% 
  mutate(feature = if_else(!(feature %in% c("gestational_age", confounders)),paste("    ",feature), feature)) %>%
  mutate(feature = gsub("_cat","",feature)) %>%
  mutate(feature = gsub("_"," ",feature)) %>%
  dplyr::select(feature, healthy_pct, psoriasis_pct) %>%
  dplyr::rename(healthy = healthy_pct, psoriasis = psoriasis_pct) %>%
  na.fill("")
```

```{r}
write.table(confounder_table, file = paste(output_dir,"confounder.txt",sep = "/"), sep = ",", quote = FALSE, row.names = F)
```

