---
title: "ABIS-psoriasis year-3 excluding auto-immune diseases"
author: "Debojyoti Das"
date: "2023-04-18"
output: html_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
curr_os <- Sys.info()["sysname"][[1]]

if (curr_os == "Windows"){
  output_dir <- "C:\\Users\\debda22\\OneDrive - Linköpings universitet\\early_nutrition\\without_auto_immune_disease\\test_3"
  # output_dir <- "C:\\Users\\debda22\\OneDrive - Linköpings universitet\\early_nutrition\\without_auto_immune_disease\\ABIS_year_3_final"
  } else {
  output_dir <- "/Users/debojyoti/OneDrive - Linköpings universitet/early_nutrition/without_auto_immune_disease/test_3" 
  # output_dir <- "/Users/debojyoti/OneDrive - Linköpings universitet/early_nutrition/without_auto_immune_disease/ABIS_year_3_final"
}

dir.create(output_dir)
```


```{r}
pacman::p_load(
  haven,        # File import
  here,         # File locator
  sjlabelled,
  janitor,      # 
  data.table,   #
  flextable,    #
  comprehenr,   # List comprehension in R
  tidyverse,    # data management + ggplot2 graphics, 
  stringr,      # manipulate text strings 
  purrr,        # loop over objects in a tidy way
  gtsummary,    # summary statistics and tests 
  broom,        # tidy up results from regressions
  lmtest,       # likelihood-ratio tests
  parameters,   # alternative to tidy up results from regressions
  see,          # alternative to visualize forest plots
  easystats,    # Forest plot
  kableExtra,
  forestplot,
  rempsyc
  )
```

load helping functions
```{r, include=FALSE}

source("all_parameters_ABIS_year_3.R", local = knitr::knit_global())
source("useful_functions_ABIS_psoriasis_no_AD.R", local = knitr::knit_global())

```

Read cohort data from SAV format file
```{r}
if (curr_os == "Windows"){
  abis_table <- read_sav("C:\\Users\\debda22\\OneDrive - Linköpings universitet\\Linkoping_projects\\ABIS_RAW_DATA_SPSS\\Variables.sav")
  cohort_table <- read_sav("C:\\Users\\debda22\\OneDrive - Linköpings universitet\\Linkoping_projects\\ABIS_RAW_DATA_SPSS\\Early_nutrition_230223.sav")
  psoriasis_diagonistic_table <- read_sav("C:\\Users\\debda22\\OneDrive - Linköpings universitet\\Linkoping_projects\\ABIS_RAW_DATA_SPSS\\L40.sav")
  } else {
  abis_table <- read_sav("/Users/debojyoti/OneDrive - Linköpings universitet/Linkoping_projects/ABIS_RAW_DATA_SPSS/Variables.sav")
  cohort_table <- read_sav("/Users/debojyoti/OneDrive - Linköpings universitet/Linkoping_projects/ABIS_RAW_DATA_SPSS/Early_nutrition_230223.sav")
  psoriasis_diagonistic_table <- read_sav("/Users/debojyoti/OneDrive - Linköpings universitet/Linkoping_projects/ABIS_RAW_DATA_SPSS/L40.sav")
  }

abis_table <- abis_table[,c("ABISnr","barn_år_mån", "ageM_cb","ageF_cb", "educationma")]

abis_table <- abis_table %>% mutate(
  child_dob = as.Date(
    as.yearmon(as.character(barn_år_mån), format = "%Y%m"))
)


cohort_table.labels <- to_vec(for (col in names(cohort_table)) 
  if(is.null(attr(cohort_table[[col]], "label"))) col 
  else attr(cohort_table[[col]], "label"))

psoriasis_diagonistic_table.labels <- 
  to_vec(for (col in names(psoriasis_diagonistic_table)) 
    if(is.null(attr(psoriasis_diagonistic_table[[col]], "label"))) col 
    else attr(psoriasis_diagonistic_table[[col]], "label"))

cohort_table_labels <- 
  data.frame("Name" = names(cohort_table), "Label" = cohort_table.labels)
psoriasis_diagonistic_labels <- 
  data.frame("Name" = names(psoriasis_diagonistic_table), 
             "Label" = psoriasis_diagonistic_table.labels)

```

add child birth date to cohort data
```{r}
print(dim(cohort_table))

cohort_table <- left_join(cohort_table, 
                             abis_table,
                             by = "ABISnr")
print(dim(cohort_table))
```

columns of interest for 3rd year
```{r}
if ( curr_os == "Windows"){
  columns_of_interest_file <- "C:\\Users\\debda22\\Documents\\Linkoping_projects\\ABIS_RAW_DATA_SPSS\\early_nutrition_1_and_3_years.xlsx"
} else {
  columns_of_interest_file <- "/Users/debojyoti/OneDrive - Linköpings universitet/Linkoping_projects/ABIS_RAW_DATA_SPSS/early_nutrition_1_and_3_years.xlsx"
}
columns_of_interest <- readxl::read_excel(
  columns_of_interest_file, 
  sheet = "3 years", 
  col_names = FALSE
  )

columns_of_interest <- rbind(columns_of_interest, c("ABISnr", "ABIS number"))
columns_of_interest <- rbind(columns_of_interest, c("Gender", "Gender"))
columns_of_interest <- rbind(columns_of_interest, c("AutoimmDisease", "AutoimmuneDisease"))
columns_of_interest <- rbind(columns_of_interest, c("child_dob", "Birth of children year and month"))


colnames(columns_of_interest) <- c("Name", "Label")
columns_of_interest <- columns_of_interest[!(columns_of_interest$Name %in% c("c_17", "c_18", "c_19", "c_20", "c_21")),]

```


drop variables absent in the data
```{r}
columns_of_interest <- columns_of_interest[!(columns_of_interest$Name %in% c("c_17", 
                                                                             "c_18", 
                                                                             "c_19", 
                                                                             "c_20", 
                                                                             "c_21", 
                                                                             "c_29txt",
                                                                             "c_110",
                                                                             "c_112", 
                                                                             "c_113_1",
                                                                             "c_117txt", 
                                                                             "c_117tx",
                                                                             "c_117_1", 
                                                                             "c_117_2", 
                                                                             "c_117_3")),]

```


Retain only columns of interest
```{r}

cohort_table <- cohort_table %>% select(columns_of_interest$Name)

```


Merge the cohort data to include psoriasis diagonistics
```{r}
psoriasis_data_full <- left_join(cohort_table, 
                             psoriasis_diagonistic_table,
                             by = "ABISnr") %>% 
  mutate(Diagnos = replace(Diagnos, is.na(Diagnos), "")) %>%
  # reformat the date (of detection)
  mutate(
    first_detection = as.Date(as.character(övFörsta), format = "%Y%m%d"), 
    second_detection = as.Date(as.character(övSenaste), format = "%Y%m%d")
    ) %>%
  mutate(
    age_first_detection = lubridate::time_length(
      difftime(first_detection,child_dob), "years"),
    age_second_detection = lubridate::time_length(
      difftime(second_detection,child_dob), "years")
  )

```

Remove attributes
```{r}

for (col in names(psoriasis_data_full)) {
  if(!(is.null(attr(psoriasis_data_full[[col]], "label")))){
    attr(psoriasis_data_full[[col]], "label") <- NULL
  }
  if(!(is.null(attr(psoriasis_data_full[[col]], "labels")))){
    attr(psoriasis_data_full[[col]], "labels") <- NULL
  }
  if(!(is.null(attr(psoriasis_data_full[[col]], "format.spss")))){
    attr(psoriasis_data_full[[col]], "format.spss") <- NULL
  }  
  if(!(is.null(attr(psoriasis_data_full[[col]], "names")))){
    attr(psoriasis_data_full[[col]], "names") <- NULL
  } 
  if(!(is.null(attr(psoriasis_data_full[[col]], "display_width")))){
    attr(psoriasis_data_full[[col]], "display_width") <- NULL
  }   
}

attr(psoriasis_data_full, "notes") <- NULL


for (col in names(psoriasis_data_full)) {
  if(is.labelled(psoriasis_data_full[[col]])){
    
    psoriasis_data_full[col] <- unlabel(psoriasis_data_full[[col]])
    
  }
  
}


psoriasis_data_full <- as.data.frame(psoriasis_data_full)

```

Store explanatory variables
We store the names of the explanatory columns as a character vector. 
This will be referenced later.


## define variables of interest 
```{r}
explanatory_vars <- c(
  "c_22", 
  "c_28",
  "c_29",
  "c_103",
  "c_104",
  "c_105",
  "c_106",
  "c_109a",
  "c_109b",
  "c_109d",
  "c_109e",
  "c_109f",
  "c_109g",
  "c_109h",
  "c_109i",
  "c_109j",
  "c_109k",
  "c_109l",
  "c_109m",
  "c_109n",
  "c_109o",
  "c_109p",
  "c_109q",
  "c_109r",
  "c_109s",
  "c_109t",
  "c_109u",
  "c_109v",
  "c_109w",
  "c_109x",
  "c_109y",
  "c_109z",
  "c_109å",
  "c_109ä",
  "c_109ö",
  "c_114",
  "c_116",
  "Gender")

```

convert dichotomous variables to 0/1 
```{r}
psoriasis_data_full <- psoriasis_data_full %>%  
  mutate(across(                                      
    .cols = all_of(c("Diagnos")),  ## for each column listed and "outcome"
    .fns = ~case_when(                              
      . %in% c("L40") ~ 1,  ## recode L40 (psoriasis diagnosis) to 1
      . %in% c("") ~ 0,       ## not present  to 0
      TRUE ~ NA_real_)        ## otherwise set to missing
    )
  )
```

remove non cases with other auto immune diseases other than psoriasis
```{r}
print("number of participants with other autoimmune diseases")
print(
  nrow(
    psoriasis_data_full[
      which((
        (psoriasis_data_full$AutoimmDisease == 1)&
          (psoriasis_data_full$Diagnos != 1))),]))

print("number of participants before filtering")
print(nrow(psoriasis_data_full))

psoriasis_data_full <- psoriasis_data_full %>% 
  filter(!((AutoimmDisease == 1)&(Diagnos != 1)))

print(nrow(psoriasis_data_full))
```


subset data to include only variables of interest and outcome
```{r}
psoriasis_data <- psoriasis_data_full[,c("ABISnr", 
                                         explanatory_vars,
                                         "age_first_detection",
                                         "age_second_detection",
                                         "Diagnos")]

psoriasis_data <- psoriasis_data %>% 
  mutate(fish = pmin(c_109d,c_109e,c_109f, na.rm = TRUE))

psoriasis_data_full <- psoriasis_data_full[,c(
  "ABISnr", explanatory_vars, "Diagnos")]


```


drop rows with missing information for variables of interest
```{r}
print("The number of rows remaining in psoriasis data") 
nrow(psoriasis_data_full)

psoriasis_data_full <- psoriasis_data_full %>% 
  drop_na(any_of(c("ABISnr", "Diagnos")))

print("Total number of rows in psoriasis data") 
nrow(psoriasis_data_full)
```
custom create variable fish intake from any source and add to list of variables of interest
```{r}
psoriasis_data_full <- psoriasis_data_full %>% 
  mutate(fish = pmin(c_109d,c_109e,c_109f, na.rm = TRUE))
explanatory_vars <- c(explanatory_vars, "fish")
```



```{r}
explanatory_vars_cats <- names(
  psoriasis_data_full)[!(names(psoriasis_data_full) %in% 
                           c("ABISnr", "fish", "Diagnos"))]

```

variable value label correspondence data frame
```{r}
explanatory_vars_df <- data.frame(
  v = character(), 
  v_labels = character(),
  labels = character()
  )


for (col in explanatory_vars_cats){
  v <-list(col)
  v_labels <- list(attr(cohort_table[[col]], "labels"))
  curr_dt <- data.frame(I(v[[1]]), I(v_labels[[1]]))
  curr_dt[["labels"]] <- rownames(curr_dt)
  
  explanatory_vars_df <- rbind(explanatory_vars_df,curr_dt)
}

rownames(explanatory_vars_df) <- seq(1,dim(explanatory_vars_df)[1])
colnames(explanatory_vars_df) <- c("variable", "value", "label")

```


```{r}
explanatory_vars_df <- explanatory_vars_df %>% 
  rbind(list(variable = rep("fish",4), value = seq(1,4), 
             label = c("daily","3-5 times/week","1-2 times/week", "seldom")
             )
        )
explanatory_vars_cats <- c(explanatory_vars_cats, "fish")
```


Looping multiple univariate models

```{r}
all_parameters <- all_parameters[all_parameters$category_variable != "milk_product",]

variables2exclude <- c("ABISnr", 
          "age_first_detection", 
          "age_second_detection", 
          "age_first_detection_cat",
          "Diagnos")

data2process <- psoriasis_data_full

output <- univariate_regression(data2process, variables2exclude)
final_univ_tab_tidy <- output[[1]]
frq_table_final_univ <- output[[2]]

final_univ_tab_tidy <- final_univ_tab_tidy %>% 
  add_header_row(
    values = c("Univariate regression: All genders but without other AD"), 
    colwidths = 8)

```


```{r}
final_univ_tab_tidy

```

# Multivariable logistic regression
multivarible regression using variables that were significant in univariate regression

```{r}
multivar_data <- psoriasis_data_full[,c("ABISnr", "c_22",  "c_106", "c_109e",
                                        "Gender", "Diagnos")]

multivar_explanatory_vars <- c("c_22", "c_106", "c_109e", "Gender")

multivar_explanatory_vars_cats <- c("other_disability_or_disease", 
                                    "milk_product_alternate_ref",
                                    "fish_Baltic", 
                                    "Gender_cat")

multivar_data <- multivariable_regression_prep(multivar_data,
                                          multivar_explanatory_vars,
                                          multivar_explanatory_vars_cats)
  
final_data <- multivariable_regression_table(
  multivar_data,
  multivar_explanatory_vars_cats)

final_data <- final_data %>% 
  add_header_row(
    values = c("Multivariable regression: All genders but without other AD"), 
    colwidths = 6)


```

participants with other disability or disease
```{r}
original_multivar_data <- multivar_data
multivar_data[(multivar_data$c_22 == 1) & (multivar_data$Diagnos == 1),]

```



save the merged table
\newpage
```{r}

final_univ_tab_tidy

```

\newpage
```{r}

final_data

```


```{r}
# p1 <- cumulative_percentage(multivar_data, 
#                       "Diagnos", 
#                       "b_5", 
#                       "psoriasis",
#                       inverse_cumul = TRUE)
# 
# p2 <- cumulative_percentage(multivar_data, 
#                       "Diagnos", 
#                       "b_6", 
#                       "psoriasis")
# 
# # p3 <- cumulative_percentage(multivar_data, 
# #                       "Diagnos", 
# #                       "b_8", 
# #                       "psoriasis")
# 
# # p4 <- cumulative_percentage(multivar_data, 
# #                       "Diagnos", 
# #                       "b_9", 
# #                       "psoriasis")
# 
# p5 <- cumulative_percentage(multivar_data, 
#                       "Diagnos", 
#                       "b_10", 
#                       "psoriasis",
#                       inverse_cumul = TRUE)

```


plot cumulative percentage to file
```{r}
# 
# pdf(paste(output_dir,"ABIS_3_year_early_nutrition_psoriasis_cumulative_percentage.pdf", sep = "/")
# )
# 
# # for (p in list(p1,p2,p3,p4,p5)) {
# for (p in list(p1,p2,p5)) {
#   print(p)
# }
# 
# dev.off()

```

correlation and plot residuals
```{r}
pdf(
  paste(
    output_dir,
    "chi_sq_test_and_percentage_breakdown_early_nutrition_year_3_multivarible.pdf",
    sep = "/")
    )

for (col in multivar_explanatory_vars_cats) {
  dt <- trends(multivar_data, col)
  
  print(dt[[1]])
}

dev.off()
  
```
save the tables
```{r}
  
flextable::save_as_html(
  final_univ_tab_tidy, 
  path = paste(output_dir,"univariate_table_year_3_ABIS.html", sep = "/")
  )
flextable::save_as_docx(
  final_univ_tab_tidy, 
  path = paste(output_dir,"univariate_table_year_3_ABIS.docx", sep = "/")
  )



flextable::save_as_docx(
  final_data, 
  path = paste(output_dir,"multivariable_table_year_3_ABIS.docx", sep = "/")
  )
flextable::save_as_html(
  final_data, 
  path = paste(output_dir,"multivariable_table_year_3_ABIS.html", sep = "/")
  )

```

median age of psoriasis detection
```{r}
puberty_age = 13

median_age <- summary(psoriasis_data$age_first_detection)[3]
median_age <- round(median_age, digits = 2)

print(paste("Median age of psoriasis detection", 
            as.character(round(median_age,digits = 2))))

```

# Data subset 
# below and above median age for diagnosis, and also 
# before and after early puberty that is  below and above 13 years of age

# Univariate Logistic Regression

subset of data
```{r}

lower_age_puberty <- paste("psoriasis before age", as.character(puberty_age))
upper_age_puberty <- paste("psoriasis after age", as.character(puberty_age))

psoriasis_data_puberty <- psoriasis_data %>% 
  mutate(age_first_detection_cat = case_when(
    age_first_detection < puberty_age ~ lower_age_puberty,
    age_first_detection >= puberty_age ~ upper_age_puberty, 
    TRUE ~ "Not detected")
    )
```


subgroups: puberty age psoriasis detection data set
```{r}
psoriasis_data_lt_puberty <- psoriasis_data_puberty %>%
  filter(age_first_detection_cat %in% c(lower_age_puberty, "Not detected"))

psoriasis_data_lt_puberty$age_first_detection_cat <- factor(
  psoriasis_data_lt_puberty$age_first_detection_cat)

print(nrow(psoriasis_data_lt_puberty))

psoriasis_data_gt_puberty <- psoriasis_data_puberty %>% 
  filter(age_first_detection_cat %in% c(upper_age_puberty, "Not detected"))

psoriasis_data_gt_puberty$age_first_detection_cat <- factor(
  psoriasis_data_gt_puberty$age_first_detection_cat)

print(nrow(psoriasis_data_gt_puberty))
```

psoriasis cases split for puberty age detection data
```{r}
print("psoriasis cases median")
nrow(psoriasis_data_puberty[psoriasis_data_puberty$Diagnos == 1,])

print(paste("psoriasis cases < ", as.character(puberty_age)))
nrow(psoriasis_data_lt_puberty[psoriasis_data_lt_puberty$Diagnos == 1,])

print(paste("psoriasis cases > ", as.character(puberty_age)))
nrow(psoriasis_data_gt_puberty[psoriasis_data_gt_puberty$Diagnos == 1,])
```

restore the levels for the variables of interest
```{r}
all_parameters <- load_all_parameter()
```

# age >= puberty age
```{r}
all_parameters[all_parameters$category_variable == "cakes_pastry_biscuits",]$labels[[1]] <- c("3-5 times/week - daily","1-2 times/week - seldom")
all_parameters[all_parameters$category_variable == "cakes_pastry_biscuits",]$breaks[[1]] <- c(0,2,4)

all_parameters[all_parameters$category_variable == "ice_cream",]$labels[[1]] <- c("1-2/3-5 times/week daily", "seldom")
all_parameters[all_parameters$category_variable == "ice_cream",]$breaks[[1]] <- c(0,3,4)

all_parameters[all_parameters$category_variable == "milk_product_alternate_ref",]$labels[[1]] <- c("nothing to 1-2 dl", "3-6 dl", "7-10 dl/ more")
all_parameters[all_parameters$category_variable == "milk_product_alternate_ref",]$breaks[[1]] <- c(0,2,3,5)

all_parameters <- all_parameters[all_parameters$category_variable != "milk_product",]

all_parameters[all_parameters$category_variable == "fish_Baltic",]$labels[[1]] <- c("1-2/3-5 times/week daily", "seldom")
all_parameters[all_parameters$category_variable == "fish_Baltic",]$breaks[[1]] <- c(0,3,4)

variables2exclude <- c("ABISnr", 
          "age_first_detection", 
          "age_second_detection",
          "age_first_detection_cat",
          "Diagnos")

data2process <- psoriasis_data_gt_puberty

output <- univariate_regression(data2process, variables2exclude)
univ_table_gt_puberty <- output[[1]]
frq_table_gt_puberty <- output[[2]]

univ_table_gt_puberty <- univ_table_gt_puberty %>% 
  add_header_row(
    values = c(paste("Univariate regression: Detected with psoriasis ",
               as.character(puberty_age)," years or older")), 
    colwidths = 8)
```


```{r}
multivar_data <- psoriasis_data_gt_puberty[,c("ABISnr","c_22", 
                                              "Gender", "Diagnos")]

multivar_explanatory_vars <- c("c_22", "Gender")

multivar_explanatory_vars_cats <- c("other_disability_or_disease",
                                    "Gender_cat")

multivar_data <- multivariable_regression_prep(multivar_data,
                                          multivar_explanatory_vars,
                                          multivar_explanatory_vars_cats)
  
multivariable_regression_gt_puberty <- multivariable_regression_table(
  multivar_data,
  multivar_explanatory_vars_cats)

multivariable_regression_gt_puberty <- multivariable_regression_gt_puberty %>% 
  add_header_row(
    values = c(paste("Multivariable regression: Detected with psoriasis ",
               as.character(puberty_age)," years or older")), 
    colwidths = 6)
```
restore the levels for the variables of interest
```{r}
all_parameters <- load_all_parameter()
```

# age < puberty age
```{r}

all_parameters[all_parameters$category_variable == "fish_Baltic",]$labels[[1]] <- c("1-2/3-5 times/week daily", "seldom")
all_parameters[all_parameters$category_variable == "fish_Baltic",]$breaks[[1]] <- c(0,3,4)

all_parameters[all_parameters$category_variable == "fish_cat_year_3",]$labels[[1]] <- c("1-2/3-5 times/week daily", "seldom")
all_parameters[all_parameters$category_variable == "fish_cat_year_3",]$breaks[[1]] <- c(0,3,4)

all_parameters[all_parameters$category_variable == "macaroni_spaghetti",]$labels[[1]] <- c("3-5 times/week - daily","1-2 times/week - seldom")
all_parameters[all_parameters$category_variable == "macaroni_spaghetti",]$breaks[[1]] <- c(0,2,4)

all_parameters[all_parameters$category_variable == "cornflakes_muesli",]$labels[[1]] <- c("3-5 times/week - daily","1-2 times/week - seldom")
all_parameters[all_parameters$category_variable == "cornflakes_muesli",]$breaks[[1]] <- c(0,2,4)


all_parameters[all_parameters$category_variable == "sausage",]$labels[[1]] <- c("3-5 times/week - daily","1-2 times/week - seldom")
all_parameters[all_parameters$category_variable == "sausage",]$breaks[[1]] <- c(0,2,4)

all_parameters[all_parameters$category_variable == "sandwich_fat",]$labels[[1]] <- c("75% fat margarine","low fat margarine/no fat")
all_parameters[all_parameters$category_variable == "sandwich_fat",]$breaks[[1]] <- c(0,1,3)

all_parameters[all_parameters$category_variable == "cakes_pastry_biscuits",]$labels[[1]] <- c("3-5 times/week - daily","1-2 times/week - seldom")
all_parameters[all_parameters$category_variable == "cakes_pastry_biscuits",]$breaks[[1]] <- c(0,2,4)


all_parameters <- all_parameters[all_parameters$category_variable != "fish_cat_dichotomous",]
  
variables2exclude <- c("ABISnr", 
          "age_first_detection", 
          "age_second_detection", 
          "age_first_detection_cat",
          "Diagnos")

data2process <- psoriasis_data_lt_puberty

output <- univariate_regression(data2process, variables2exclude)
univ_table_lt_puberty <- output[[1]]
frq_table_lt_puberty <- output[[2]]

univ_table_lt_puberty <- univ_table_lt_puberty %>% 
  add_header_row(
    values = c(paste("Univariate regression: Detected with psoriasis before",
               as.character(puberty_age)," years ")), 
    colwidths = 8)
```


```{r}
multivar_data <- psoriasis_data_lt_puberty[,c("ABISnr", "c_109e", 
                                               "Gender","Diagnos")]

multivar_explanatory_vars <- c("c_109e", "Gender")

multivar_explanatory_vars_cats <-  c("fish_Baltic",
                                     "Gender_cat")

multivar_data <- multivariable_regression_prep(multivar_data,
                                          multivar_explanatory_vars,
                                          multivar_explanatory_vars_cats)
  
multivariable_regression_lt_puberty <- multivariable_regression_table(
  multivar_data,
  multivar_explanatory_vars_cats)

multivariable_regression_lt_puberty <- multivariable_regression_lt_puberty %>% 
  add_header_row(
    values = c(paste("Multivariable regression: Detected with psoriasis before",
               as.character(puberty_age)," years")), 
    colwidths = 6)
```

```{r}
# detection_gt_puberty
univariate_table <- univ_table_gt_puberty

flextable::save_as_docx(
  univariate_table, 
  path = paste(output_dir,"univariate_table_gt_puberty_year_3_ABIS.docx", sep = "/")
  )
flextable::save_as_html(
  univariate_table, 
  path = paste(output_dir,"univariate_table_gt_puberty_year_3_ABIS.html", sep = "/")
  )

multivariate_table <- multivariable_regression_gt_puberty

flextable::save_as_docx(
  multivariate_table, 
  path = paste(output_dir,"multivariate_table_gt_puberty_year_3_ABIS.docx", sep = "/")
  )
flextable::save_as_html(
  multivariate_table, 
  path = paste(output_dir,"multivariate_table_gt_puberty_year_3_ABIS.html", sep = "/")
  )
```


```{r}
# detection_lt_puberty
univariate_table <- univ_table_lt_puberty

flextable::save_as_docx(
  univariate_table, 
  path = paste(output_dir,"univariate_table_lt_puberty_year_3_ABIS.docx", sep = "/")
  )
flextable::save_as_html(
  univariate_table, 
  path = paste(output_dir,"univariate_table_lt_puberty_year_3_ABIS.html", sep = "/")
  )

multivariate_table <- multivariable_regression_lt_puberty

flextable::save_as_docx(
  multivariate_table, 
  path = paste(output_dir,"multivariate_table_lt_puberty_year_3_ABIS.docx", sep = "/")
  )
flextable::save_as_html(
  multivariate_table, 
  path = paste(output_dir,"multivariate_table_lt_puberty_year_3_ABIS.html", sep = "/")
  )
```


```{r}
psoriasis_data_boys <- psoriasis_data %>% filter(Gender == 0)
psoriasis_data_girls <- psoriasis_data %>% filter(Gender == 1)

print("number of boy participant")
print(nrow(psoriasis_data_boys))

print("number of psoriasis cases in boys")
print(nrow(psoriasis_data_boys[psoriasis_data_boys$Diagnos == 1,]))

print("number of girl participant")
print(nrow(psoriasis_data_girls))

print("number of psoriasis cases in girls")
print(nrow(psoriasis_data_girls[psoriasis_data_girls$Diagnos == 1,]))
```
restore the levels for the variables of interest
```{r}
all_parameters <- load_all_parameter()
```


# boys only
```{r}
all_parameters <-all_parameters[all_parameters$category_variable != "milk_product",]

all_parameters[all_parameters$category_variable == "milk_product_alternate_ref",]$labels[[1]] <- c("nothing/ 1-2 dl", "3-6 dl","7-10 dl", "more than 1 litre")
all_parameters[all_parameters$category_variable == "milk_product_alternate_ref",]$breaks[[1]] <- c(0,2,3,4,5)
# 
milk_alt_ref = "nothing/ 1-2 dl"

all_parameters[all_parameters$category_variable == "fish_lake",]$labels[[1]] <- c("1-2/3-5 times/week - daily", "seldom")
all_parameters[all_parameters$category_variable == "fish_lake",]$breaks[[1]] <- c(0,3,4)

all_parameters[all_parameters$category_variable == "fish_Baltic",]$labels[[1]] <- c("1-2/3-5  times/week - daily", "seldom")
all_parameters[all_parameters$category_variable == "fish_Baltic",]$breaks[[1]] <- c(0,3,4)

all_parameters[all_parameters$category_variable == "fish_cat_year_3",]$labels[[1]] <- c("1-2/3-5 times/week - daily", "seldom")
all_parameters[all_parameters$category_variable == "fish_cat_year_3",]$breaks[[1]] <- c(0,3,4)

all_parameters <-all_parameters[all_parameters$category_variable != "fish_cat_dichotomous",]

all_parameters <-all_parameters[all_parameters$category_variable != "red_meat_dichotomous",]

all_parameters <-all_parameters[all_parameters$category_variable != "candy",]

all_parameters[all_parameters$category_variable == "heavy_creme",]$labels[[1]] <- c("1-2/3-5 times/week - daily", "seldom")
all_parameters[all_parameters$category_variable == "heavy_creme",]$breaks[[1]] <- c(0,3,4)


all_parameters[all_parameters$category_variable == "cakes_pastry_biscuits",]$labels[[1]] <- c("3-5 times/week - daily","1-2 times/week - seldom")
all_parameters[all_parameters$category_variable == "cakes_pastry_biscuits",]$breaks[[1]] <- c(0,2,4)


all_parameters[all_parameters$category_variable == "chocolate_candy_bar",]$labels[[1]] <- c("1-2/3-5 times/week - daily","seldom")
all_parameters[all_parameters$category_variable == "chocolate_candy_bar",]$breaks[[1]] <- c(0,3,4)

all_parameters[all_parameters$category_variable == "cornflakes_muesli",]$labels[[1]] <- c("3-5 times/week - daily","1-2 times/week - seldom")
all_parameters[all_parameters$category_variable == "cornflakes_muesli",]$breaks[[1]] <- c(0,2,4)

all_parameters <- all_parameters[all_parameters$variable2categorise != "Gender",]

variables2exclude <- c("ABISnr", 
          "age_first_detection", 
          "age_second_detection",
          "age_first_detection_cat",
          "Gender",
          "Diagnos")

data2process <- psoriasis_data_boys

output <- univariate_regression(data2process, 
                                variables2exclude,
                                milk_alt_ref = milk_alt_ref)
univ_table_boys <- output[[1]]
frq_table_boys <- output[[2]]

univ_table_boys <- univ_table_boys %>% 
  add_header_row(
    values = c("Univariate regression: Detected with psoriasis in boys"), 
    colwidths = 8)
```

## for boys only "other_disability_or_disease was found to be significant in univariate regression

restore the levels for the variables of interest
```{r}
all_parameters <- load_all_parameter()
```

# girls only
```{r}
all_parameters <- all_parameters[all_parameters$variable2categorise != "Gender",]
all_parameters <- all_parameters[all_parameters$category_variable != "macaroni_spaghetti",]

all_parameters[all_parameters$category_variable == "sandwich_fat",]$labels[[1]] <- c("75% fat margarine","low fat margarine/no fat")
all_parameters[all_parameters$category_variable == "sandwich_fat",]$breaks[[1]] <- c(0,1,3)

all_parameters[all_parameters$category_variable == "fish_Baltic",]$labels[[1]] <- c("1-2/3-5 times/week - daily", "seldom")
all_parameters[all_parameters$category_variable == "fish_Baltic",]$breaks[[1]] <- c(0,3,4)

all_parameters <- all_parameters[all_parameters$category_variable != "candy",]

all_parameters[all_parameters$category_variable == "fruit_drinks",]$labels[[1]] <- c("3-5 times/week - daily","1-2 times/week/ seldom")
all_parameters[all_parameters$category_variable == "fruit_drinks",]$breaks[[1]] <- c(0,2,4)

variables2exclude <- c("ABISnr", 
          "age_first_detection", 
          "age_second_detection", 
          "age_first_detection_cat",
          "c_109v", #"macaroni_spaghetti"
          "Gender",
          "Diagnos")

data2process <- psoriasis_data_girls

output <- univariate_regression(data2process, variables2exclude)
univ_table_girls <- output[[1]]
frq_table_girls <- output[[2]]

univ_table_girls <- univ_table_girls %>% 
  add_header_row(
    values = c("Univariate regression: Detected with psoriasis in girls"), 
    colwidths = 8)
```


```{r}
# detection_boys
univariate_table <- univ_table_boys

flextable::save_as_docx(
  univariate_table, 
  path = paste(output_dir,"univariate_table_boys_year_3_ABIS.docx", sep = "/")
  )
flextable::save_as_html(
  univariate_table, 
  path = paste(output_dir,"univariate_table_boys_year_3_ABIS.html", sep = "/")
  )

```


```{r}
# detection_girls
univariate_table <- univ_table_girls

flextable::save_as_docx(
  univariate_table, 
  path = paste(output_dir,"univariate_table_girls_year_3_ABIS.docx", sep = "/")
  )
flextable::save_as_html(
  univariate_table, 
  path = paste(output_dir,"univariate_table_girls_year_3_ABIS.html", sep = "/")
  )


```

restore the levels for the variables of interest
```{r}
all_parameters <- load_all_parameter()
```



