---
title: "Healthy Eating Index (HEI): ABIS-psoriasis data excluding auto-immune diseases"
author: "Debojyoti Das"
date: "2023-04-18"
output:
  html_document: default
  pdf_document: default
---

```{r}
source("C://Users/debda22/OneDrive - Linköpings universitet/Rmd_and_R_files/Functions_rmph.R")
```

```{r setup, include=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = TRUE)
dir.create("C:/Users/debda22/OneDrive - Linköpings universitet/early_nutrition/healthy_eating_index_results")

 # source("C:/Users/debda22/OneDrive - Linköpings universitet/Rmd_and_R_files/useful_functions_ABIS_psoriasis_no_AD.R", local = knitr::knit_global())
```


```{r}
pacman::p_load(
  haven,        # File import
  here,         # File locator
  sjlabelled,
  janitor,      # 
  data.table,   #
  flextable,    #
  comprehenr,   # List comprehension in R
  tidyverse,    # data management + ggplot2 graphics, 
  stringr,      # manipulate text strings 
  purrr,        # loop over objects in a tidy way
  gtsummary,    # summary statistics and tests 
  broom,        # tidy up results from regressions
  lmtest,       # likelihood-ratio tests
  parameters,   # alternative to tidy up results from regressions
  see,          # alternative to visualize forest plots
  easystats,    # Forest plot
  kableExtra,
  forestplot,
  rempsyc,
  mice,
  parallel
  )
```

Read cohort data from SAV format file

```{r}
curr_os <- Sys.info()["sysname"][[1]]

if (curr_os == "Windows"){
  abis_table <- read_sav("C:\\Users\\debda22\\OneDrive - Linköpings universitet\\Linkoping_projects\\ABIS_RAW_DATA_SPSS\\ABIS_data_base.sav")
  # cohort_table <- read_sav("C:\\Users\\debda22\\OneDrive - Linköpings universitet\\Linkoping_projects\\ABIS_RAW_DATA_SPSS\\Early_nutrition_230223.sav")
  psoriasis_diagonistic_table <- read_sav("C:\\Users\\debda22\\OneDrive - Linköpings universitet\\Linkoping_projects\\ABIS_RAW_DATA_SPSS\\L40_corrected.sav")
  } else {
  abis_table <- read_sav("/Users/debojyoti/OneDrive - Linköpings universitet/Linkoping_projects/ABIS_RAW_DATA_SPSS/ABIS_data_base.sav")
  # cohort_table <- read_sav("/Users/debojyoti/OneDrive - Linköpings universitet/Linkoping_projects/ABIS_RAW_DATA_SPSS/Early_nutrition_230223.sav")
  psoriasis_diagonistic_table <- read_sav("/Users/debojyoti/OneDrive - Linköpings universitet/Linkoping_projects/ABIS_RAW_DATA_SPSS/L40_corrected.sav")
  }
```


food groups classification
```{r}
fruits_vegetables <- c("b_53", 
                       "c_109å", 
                       "b_54", 
                       "c_109a", 
                       "b_63", 
                       "c_109l")
fruits_vegetables_cats <- c("fruits_1y", 
                            "fruits_3y", 
                            "vegetables_1y", 
                            "vegetables_3y",
                            "mushrooms_1y",
                            "mushrooms_3y")

dairy_food <- c("b_97",
                "c_114", 
                "b_99",
                "c_116", 
                "b_101",
                "c_109o")
dairy_food_cats <- c("milk_1y",
                     "milk_3y",
                     "yoghurt_1y",
                     "yoghurt_3y",
                     "cheese_1y",
                     "cheese_3y")

red_meat_and_meat_product <- c("b_60",
                                "c_109h", 
                                "b_61",
                                "c_109i", 
                                "b_62",
                                "c_109j",
                                "c_109k")
red_meat_and_meat_product_cats <- c("game_1y",
                                "game_3y", 
                                "beef_1y",
                                "beef_3y", 
                                "pork_1y",
                                "pork_3y",
                                "sausage_3y")

fish_and_egg <- c("b_56", 
                  "c_109d", 
                  "b_57", 
                  "c_109e", 
                  "b_58", 
                  "c_109f", 
                  "b_59", 
                  "c_109g")
fish_and_egg_cats <- c("fish_lake_1y",
                       "fish_lake_3y",
                       "fish_Baltic_1y",
                       "fish_Baltic_3y",
                       "fish_other_1y",
                       "fish_other_3y",
                       "eggs_1y",
                       "eggs_3y")

soft_drinks <- c("b_94", "c_109z")
soft_drinks_cats <- c("juice_1y", "juice_3y")

salty_snacks <- c("b_67","c_109n", "c_109w")
salty_snacks_cats <- c("chips_1y","chips_3y","popcorn_3y")

sweet_snacks <- c("b_65", 
                  "c_109q", 
                  "b_66",
                  "c_109r", 
                  "b_68",
                  "c_109p", 
                  "c_109y")
sweet_snacks_cats <- c("chocolate_1y", 
                       "chocolate_3y",
                       "other_candy_1y",
                       "other_candy_3y",
                       "dessert_1y",
                       "dessert_3y",
                       "ice_cream_3y")
```

columns of interest
```{r}
columns_of_interest <- data.frame(
  Name = c("ABISnr",
           "Gender",
           fruits_vegetables, 
           dairy_food,
           red_meat_and_meat_product,
           fish_and_egg,
           soft_drinks,
           salty_snacks,
           sweet_snacks),
  Labels = c("ABIS number",
             "Gender",
             fruits_vegetables_cats,
             dairy_food_cats,
             red_meat_and_meat_product_cats,
             fish_and_egg_cats,
             soft_drinks_cats,
             salty_snacks_cats,
             sweet_snacks_cats)
)

```



```{r}
abis_table <- abis_table[,columns_of_interest$Name]

abis_table.labels <- to_vec(for (col in names(abis_table)) 
  if(is.null(attr(abis_table[[col]], "label"))) col 
  else attr(abis_table[[col]], "label"))

psoriasis_diagonistic_table.labels <- 
  to_vec(for (col in names(psoriasis_diagonistic_table)) 
    if(is.null(attr(psoriasis_diagonistic_table[[col]], "label"))) col 
    else attr(psoriasis_diagonistic_table[[col]], "label"))

abis_table_labels <- 
  data.frame("Name" = names(abis_table), "Label" = abis_table.labels)
psoriasis_diagonistic_labels <- 
  data.frame("Name" = names(psoriasis_diagonistic_table), 
             "Label" = psoriasis_diagonistic_table.labels)

```

Merge the data to include psoriasis diagonistics

```{r}
psoriasis_data_full <- full_join(abis_table, 
                             psoriasis_diagonistic_table,
                             by = "ABISnr") %>% 
  mutate(Diagnos = replace(Diagnos, is.na(Diagnos), "")) 

```

Remove attributes

```{r}

for (col in names(psoriasis_data_full)) {
  if(!(is.null(attr(psoriasis_data_full[[col]], "label")))){
    attr(psoriasis_data_full[[col]], "label") <- NULL
  }
  if(!(is.null(attr(psoriasis_data_full[[col]], "labels")))){
    attr(psoriasis_data_full[[col]], "labels") <- NULL
  }
  if(!(is.null(attr(psoriasis_data_full[[col]], "format.spss")))){
    attr(psoriasis_data_full[[col]], "format.spss") <- NULL
  }  
  if(!(is.null(attr(psoriasis_data_full[[col]], "names")))){
    attr(psoriasis_data_full[[col]], "names") <- NULL
  } 
  if(!(is.null(attr(psoriasis_data_full[[col]], "display_width")))){
    attr(psoriasis_data_full[[col]], "display_width") <- NULL
  }   
}

attr(psoriasis_data_full, "notes") <- NULL


for (col in names(psoriasis_data_full)) {
  if(is.labelled(psoriasis_data_full[[col]])){
    
    psoriasis_data_full[col] <- unlabel(psoriasis_data_full[[col]])
    
  }
  
}


psoriasis_data_full <- as.data.frame(psoriasis_data_full)

```



convert dichotomous variables to 0/1 
```{r}
psoriasis_data_full <- psoriasis_data_full %>%  
  mutate(across(                                      
    .cols = all_of(c("Diagnos")),  ## for each column listed and "outcome"
    .fns = ~case_when(                              
      . %in% c("L40")   ~ 1,  ## recode L40 (psoriasis diagnosis) to 1
      . %in% c("") ~ 0,       ## not present  to 0
      TRUE ~ NA_real_)        ## otherwise set to missing
    )
  )
```

remove non cases with other auto immune diseases other than psoriasis
```{r}
print(paste("number of participants with all Autoimmune diseases", 
      as.character(nrow(psoriasis_data_full))))
```


```{r}
psoriasis_data_full <- psoriasis_data_full %>% 
  filter(!((AutoimmDisease == 1)&(Diagnos != 1))) 
# %>%
#   filter(!is.na(Gender))
```


```{r}
print(paste("number of participants without other Autoimmune diseases",
      as.character(nrow(psoriasis_data_full))))
```


subset data to include only variables of interest and outcome
```{r}
psoriasis_data_full <- psoriasis_data_full %>% 
  select(-c("AutoimmDisease", "övAntal", "övFörsta", "övSenaste"))
```

factor sex and diagnosis
```{r}
psoriasis_data_full$Gender <- factor(psoriasis_data_full$Gender)
psoriasis_data_full$Diagnos <- factor(psoriasis_data_full$Diagnos)

```

recode values for food items
```{r}
food_groups <- c(fruits_vegetables,
                 dairy_food,
                 red_meat_and_meat_product,
                 fish_and_egg,
                 soft_drinks,
                 salty_snacks,
                 sweet_snacks)

food_groups_cat <- c(fruits_vegetables_cats,
                 dairy_food_cats,
                 red_meat_and_meat_product_cats,
                 fish_and_egg_cats,
                 soft_drinks_cats,
                 salty_snacks_cats,
                 sweet_snacks_cats)

for (i in seq_along(food_groups)) {
      
  new_column = sym(food_groups_cat[[i]])
  food = sym(food_groups[[i]])
  
  # print(food)
  # print(new_column)

  if (food_groups[[i]] %in% c("b_53",  "c_109å",
                  "b_54","c_109a",
                  "b_55", 
                  "b_56", "c_109d",
                  "b_57", "c_109e",
                  "b_58",  "c_109f",
                  "b_60", "c_109h",
                  "b_61", "c_109i",
                  "b_62", "c_109j", "c_109k",
                  "b_63", "c_109l",
                  "b_64",
                  "b_65", "c_109q", 
                  "b_66", "c_109r",
                  "b_67",
                  "b_68",
                  "b_69",
                  "b_73",
                  "b_79", 
                  "b_101", "c_109o",
                  "c_109n", "c_109w",
                  "c_109p", "c_109y"
                  )
      ){

    psoriasis_data_full <- psoriasis_data_full %>%
      mutate( !!new_column := case_when(
          !!food == 4 ~ 0.5,  # score for least intake of healthy food per week
          !!food == 3 ~ 1.5,
          !!food == 2 ~ 4,
          !!food == 1 ~ 7,
          TRUE ~ NA_real_)
        )
  }
  if (food_groups[[i]] %in% c("b_97","c_114", "b_99","c_116")){
        psoriasis_data_full <- psoriasis_data_full %>%
      mutate( !!new_column := case_when(
          !!food == 7 ~ 28, 
          !!food == 6 ~ 21, 
          !!food == 5 ~ 14, 
          !!food == 4 ~ 7, 
          !!food == 3 ~ 5,
          !!food == 2 ~ 2,
          !!food == 1 ~ 0,
          TRUE ~ NA_real_)
          )
  }
  if (food_groups[[i]] %in% c("b_94", "c_109z")){
      psoriasis_data_full <- psoriasis_data_full %>%
    mutate( !!new_column := case_when(
        !!food == 7 ~ 15, 
        !!food == 6 ~ 12, 
        !!food == 5 ~ 8.5, 
        !!food == 4 ~ 5, 
        !!food == 3 ~ 2,
        !!food == 2 ~ 0.5,
        !!food == 1 ~ 0,
        TRUE ~ NA_real_)
        )
}
  if (food_groups[[i]] %in% c("b_49")){
      psoriasis_data_full <- psoriasis_data_full %>%
    mutate( !!new_column := case_when(
        !!food == 5 ~ 60, 
        !!food == 4 ~ 56, 
        !!food == 3 ~ 28,
        !!food == 2 ~ 10.5,
        !!food == 1 ~ 0,
        TRUE ~ NA_real_)
        )
} 
  if (food_groups[[i]] %in% c("b_59",  "c_109g")){
      psoriasis_data_full <- psoriasis_data_full %>%
    mutate( !!new_column := case_when( 
        !!food == 4 ~ 0.5, 
        !!food == 3 ~ 1.5,
        !!food == 2 ~ 4,
        !!food == 1 ~ 7,
        TRUE ~ NA_real_)
        )
}   
}
```

filter out rows with no entries for any food groups
```{r}
indices_df <- psoriasis_data_full[,c(
  "milk_1y",
  "milk_3y",
  "yoghurt_1y",
  "yoghurt_3y",
  "cheese_1y",
  "cheese_3y",
  "fish_lake_1y",
  "fish_lake_3y",   
  "fish_Baltic_1y", 
  "fish_Baltic_3y", 
  "fish_other_1y",  
  "fish_other_3y",  
  "eggs_1y",        
  "eggs_3y",
  "fruits_1y",      
  "fruits_3y",      
  "vegetables_1y",  
  "vegetables_3y",  
  "mushrooms_1y",   
  "mushrooms_3y",   
  "game_1y",
  "game_3y",        
  "beef_1y",        
  "beef_3y",        
  "pork_1y",        
  "pork_3y",        
  "sausage_3y",     
  "chips_1y",      
  "chips_3y",       
  "popcorn_3y",     
  "juice_1y",       
  "juice_3y",       
  "chocolate_1y",   
  "chocolate_3y",   
  "other_candy_1y",
  "other_candy_3y", 
  "dessert_1y",   
  "dessert_3y",    
  "ice_cream_3y")]

psoriasis_data_full <- psoriasis_data_full[rowSums(is.na(indices_df)) != ncol(indices_df), ]
```

```{r}
print("Number of participants")
print(psoriasis_data_full %>% nrow())

print("Number of participants with psoriasis")
print(psoriasis_data_full %>% filter(Diagnos == 1) %>% nrow())
```

retain recoded food items only
```{r}
psoriasis_data_full <- psoriasis_data_full %>%
  select(-food_groups)
```

save original data
```{r}
original_data_with_missing_entries <- psoriasis_data_full
```

```{r}
# missingness per variable
P <-sapply(psoriasis_data_full, function(x) mean(is.na(x)))
```

impute missing entries: parallel

```{r}
number_of_imputations <- nimpute(psoriasis_data_full, method = "avg")
print("number of imputations based on mean missingness")
print(number_of_imputations)

n_core = detectCores()
number_imputation_per_core = 2

print("press second button on interactive window!!")
imp_parallel <- futuremice(
  psoriasis_data_full, 
  m = number_of_imputations,
  parallelseed = 123456,
  n.core = n_core,
  seed = 12345,
  use.logical = TRUE,
  n.imp.core = number_imputation_per_core,
  maxit = 0
  )

pred <- imp_parallel$predictorMatrix

# removes the variable ABISnr from the set of predictors, but still leaves it to be predicted by the other variables.
pred[,"ABISnr"] <- 0

```

parallel imputation run

```{r}
start_time <- Sys.time()
print("press second button on interactive window!!")

imp_parallel <- futuremice(
            psoriasis_data_full, 
            m = number_of_imputations,
            parallelseed = 123456,
            n.core = n_core,
            seed = 12345,
            use.logical = TRUE,
            n.imp.core = number_imputation_per_core,
            predictorMatrix = pred, 
            # post = post,
            maxit = 10,
            progress = TRUE)

end_time <- Sys.time()
print("parallel imputation time")
print(end_time - start_time)
```

extract imputed data

```{r}
# extract imputed data

imputed_psoriasis_data_full <- complete(imp_parallel, action = "long", include = TRUE)
original_psoriasis_data_full <- complete(imp_parallel, action = 0)
```


Compute HEI for food groups

```{r}
imputed_psoriasis_data_full <- imputed_psoriasis_data_full %>%
  group_by(.imp) %>%
  mutate(
    ######### FRUIT AND VEGETABLES ############
    # 1 year
    fruits_vegs_1y = rowSums(across(c(fruits_1y,
                         vegetables_1y,
                         mushrooms_1y)),
                         na.rm = TRUE),
    # 3 years
    fruits_vegs_3y = rowSums(across(c(fruits_3y,
                         vegetables_3y,
                         mushrooms_3y)),
                         na.rm = TRUE),
    ######### DAIRY FOODS #####################
    # 1 year
    dairy_foods_1y = rowSums(across(c(milk_1y,
                         yoghurt_1y,
                         cheese_1y)),
                         na.rm = TRUE),
    # 3 years
    dairy_foods_3y = rowSums(across(c(milk_3y,
                         yoghurt_3y,
                         cheese_3y)),
                         na.rm = TRUE),
    ######### RED MEAT AND MEAT PRODUCTS #########
    # 1 year
    red_meat_1y = rowSums(across(c(game_1y,
                     beef_1y,
                     pork_1y)),
                     na.rm = TRUE),
    # 3 years
    red_meat_3y = rowSums(across(c(game_3y,
                     beef_3y,
                     pork_3y,
                     sausage_3y)),
                     na.rm = TRUE),
    ######### WHITE MEAT AND FISH#########
    # 1 year
    white_meat_1y = rowSums(across(c(fish_lake_1y,
                        fish_Baltic_1y,
                        fish_other_1y,
                        eggs_1y)),
                        na.rm = TRUE),
    # 3 years
    white_meat_3y = rowSums(across(c(fish_lake_3y,
                        fish_Baltic_3y,
                        fish_other_3y,
                        eggs_3y)),
                        na.rm = TRUE),
    ######### SOFT DRINKS #########
    # 1 year
    soft_drinks_1y = rowSums(across(c(juice_1y)),
                         na.rm = TRUE),
    # 3 years
    soft_drinks_3y = rowSums(across(c(juice_3y)),
                     na.rm = TRUE),
    ######### SALTY SNACKS #########
    # 1 year
    salty_snacks_1y = rowSums(across(c(chips_1y)),
                          na.rm = TRUE),
    # 3 years
    salty_snacks_3y = rowSums(across(c(chips_3y,
                          popcorn_3y)),
                          na.rm = TRUE),
    ######### SWEET SNACKS#########
    # 1 year
    sweet_snacks_1y = rowSums(across(c(chocolate_1y,
                          other_candy_1y,
                          dessert_1y)),
                          na.rm = TRUE),
    # 3 years
    sweet_snacks_3y = rowSums(across(c(chocolate_3y,
                          other_candy_3y,
                          dessert_3y,
                          ice_cream_3y)),
                          na.rm = TRUE)

  )


```


```{r}
# psoriasis_data_full <- psoriasis_data_full %>%
#   mutate(
#     ######### FRUIT AND VEGETABLES ############
#     # 1 year
#     fruits_vegs_1y = rowSums(across(c(fruits_1y, 
#                          vegetables_1y, 
#                          mushrooms_1y)), 
#                          na.rm = TRUE),
#     # 3 years
#     fruits_vegs_3y = rowSums(across(c(fruits_3y, 
#                          vegetables_3y, 
#                          mushrooms_3y)), 
#                          na.rm = TRUE),
#     ######### DAIRY FOODS #####################
#     # 1 year
#     dairy_foods_1y = rowSums(across(c(milk_1y,
#                          yoghurt_1y,
#                          cheese_1y)),
#                          na.rm = TRUE),
#     # 3 years
#     dairy_foods_3y = rowSums(across(c(milk_3y,
#                          yoghurt_3y,
#                          cheese_3y)),
#                          na.rm = TRUE),
#     ######### RED MEAT AND MEAT PRODUCTS #########
#     # 1 year
#     red_meat_1y = rowSums(across(c(game_1y,
#                      beef_1y,
#                      pork_1y)),
#                      na.rm = TRUE),
#     # 3 years
#     red_meat_3y = rowSums(across(c(game_3y,
#                      beef_3y,
#                      pork_3y,
#                      sausage_3y)),
#                      na.rm = TRUE),
#     ######### WHITE MEAT AND FISH#########
#     # 1 year
#     white_meat_1y = rowSums(across(c(fish_lake_1y,
#                         fish_Baltic_1y,
#                         fish_other_1y,
#                         eggs_1y)), 
#                         na.rm = TRUE),
#     # 3 years
#     white_meat_3y = rowSums(across(c(fish_lake_3y,
#                         fish_Baltic_3y,
#                         fish_other_3y,
#                         eggs_3y)), 
#                         na.rm = TRUE),
#     ######### SOFT DRINKS #########
#     # 1 year
#     soft_drinks_1y = rowSums(across(c(juice_1y)), 
#                          na.rm = TRUE),
#     # 3 years
#     soft_drinks_3y = rowSums(across(c(juice_3y)), 
#                      na.rm = TRUE),
#     ######### SALTY SNACKS #########
#     # 1 year
#     salty_snacks_1y = rowSums(across(c(chips_1y)),
#                           na.rm = TRUE),
#     # 3 years
#     salty_snacks_3y = rowSums(across(c(chips_3y,
#                           popcorn_3y)),
#                           na.rm = TRUE),
#     ######### SWEET SNACKS#########
#     # 1 year
#     sweet_snacks_1y = rowSums(across(c(chocolate_1y,
#                           other_candy_1y)),
#                           na.rm = TRUE),
#     # 3 years
#     sweet_snacks_3y = rowSums(across(c(chocolate_3y,
#                           other_candy_3y,
#                           dessert_3y,
#                           ice_cream_3y)), 
#                           na.rm = TRUE)
# 
#   )
# 

```

filter/ remove participants with no data on any of the food groups
```{r}
# 
# print(paste("number of participants before filtering",
# as.character(nrow(psoriasis_data_full))))
# 
# psoriasis_data_full <- psoriasis_data_full[rowSums(psoriasis_data_full[,c(
#       "fruits_vegs_1y",
#       "fruits_vegs_3y",
#       "dairy_foods_1y",
#       "dairy_foods_3y",
#       "red_meat_1y",
#       "red_meat_3y",
#       "white_meat_1y",
#       "white_meat_3y",
#       "soft_drinks_1y",
#       "soft_drinks_3y",
#       "salty_snacks_1y",
#       "salty_snacks_3y",
#       "sweet_snacks_1y",
#       "sweet_snacks_3y"
#       )])>0,]
# 
# print(paste("number of participants after filtering",
# as.character(nrow(psoriasis_data_full))))
# 
# print(paste("number of participants with psoriasis after filtering",
# as.character(
#   nrow(
#     psoriasis_data_full[psoriasis_data_full$Diagnos == 1,]))))

```

healthy and unhealthy food groups
```{r}

healthy_food_groups <- c(
  "fruits_vegs_1y", 
  "fruits_vegs_3y", 
  "dairy_foods_1y",
  "dairy_foods_3y",
  "white_meat_1y",
  "white_meat_3y" 
  )
unhealthy_food_groups <- c(
  "red_meat_1y",
  "red_meat_3y", 
  "soft_drinks_1y",
  "soft_drinks_3y", 
  "salty_snacks_1y", 
  "salty_snacks_3y",
  "sweet_snacks_1y", 
  "sweet_snacks_3y"
)
```

```{r}
get_quantiles <- function(curr_vector){
  return(
    quantile(curr_vector, probs = c(0.25,0.50,0.75,1.0), na.rm = TRUE)
  )
}
```


```{r}
for (fg in healthy_food_groups) {

  fg_q = paste(fg,"_q", sep = "")
  
  fg <- sym(fg)
  fg_q <- sym(fg_q)
  
  imputed_psoriasis_data_full <- imputed_psoriasis_data_full %>%
    group_by(.imp) %>%
    mutate( !!fg_q := case_when( 
    !!fg <= get_quantiles(.data[[fg]])[[1]] ~ 1, 
    (!!fg > get_quantiles(.data[[fg]])[[1]]) & (!!fg <= get_quantiles(.data[[fg]])[[2]]) ~ 2,
    (!!fg > get_quantiles(.data[[fg]])[[2]]) & (!!fg <= get_quantiles(.data[[fg]])[[3]]) ~ 3,
    (!!fg > get_quantiles(.data[[fg]])[[3]]) & (!!fg <= get_quantiles(.data[[fg]])[[4]]) ~ 4)
    )
  
}

for (fg in unhealthy_food_groups) {

  fg_q = paste(fg,"_q", sep = "")
  
  fg <- sym(fg)
  fg_q <- sym(fg_q)
  
  imputed_psoriasis_data_full <- imputed_psoriasis_data_full %>%
    group_by(.imp) %>%
    mutate( !!fg_q := case_when( 
    !!fg <= get_quantiles(.data[[fg]])[[1]] ~ 4, 
    (!!fg > get_quantiles(.data[[fg]])[[1]]) & (!!fg <= get_quantiles(.data[[fg]])[[2]]) ~ 3,
    (!!fg > get_quantiles(.data[[fg]])[[2]]) & (!!fg <= get_quantiles(.data[[fg]])[[3]]) ~ 2,
    (!!fg > get_quantiles(.data[[fg]])[[3]]) & (!!fg <= get_quantiles(.data[[fg]])[[4]]) ~ 1)
    )
  
}

```

divide food groups into quartiles based on their intake
```{r}
# for (fg in healthy_food_groups) {
#   q = quantile(psoriasis_data_full[[fg]], 
#                probs = c(0.25,0.50,0.75,1.0))
#   q1 = q[1]
#   q2 = q[2]
#   q3 = q[3]
#   q4 = q[4]
#   
#   fg_q = paste(fg,"_q", sep = "")
#   
#   fg <- sym(fg)
#   fg_q <- sym(fg_q)
#   
#   psoriasis_data_full <- psoriasis_data_full %>%
#     mutate( !!fg_q := case_when( 
#     !!fg <= q1 ~ 1, 
#     (!!fg > q1) & (!!fg <= q2) ~ 2,
#     (!!fg > q2) & (!!fg <= q3) ~ 3,
#     (!!fg > q3) & (!!fg <= q4) ~ 4)
#     )
#   
# }
# 
# for (fg in unhealthy_food_groups) {
#   q = quantile(psoriasis_data_full[[fg]], 
#                probs = c(0.25,0.50,0.75,1.0))
#   q1 = q[1]
#   q2 = q[2]
#   q3 = q[3]
#   q4 = q[4]
#   
#   fg_q = paste(fg,"_q", sep = "")
#   
#   fg <- sym(fg)
#   fg_q <- sym(fg_q)
#   
#   psoriasis_data_full <- psoriasis_data_full %>%
#     mutate( !!fg_q := case_when( 
#     !!fg <= q1 ~ 4, 
#     (!!fg > q1) & (!!fg <= q2) ~ 3,
#     (!!fg > q2) & (!!fg <= q3) ~ 2,
#     (!!fg > q3) & (!!fg <= q4) ~ 1)
#     )
#   
# }
```

compute total Healthy Eating Index (HEI)
```{r}
year_1_list <- c()
year_3_list <- c()

quartile_columns <- names(imputed_psoriasis_data_full)[to_vec(for (i in names(imputed_psoriasis_data_full)) grepl("_q$",i))]

for (f in quartile_columns) {
  if(length(grep("_1y",f)) != 0){
    year_1_list <- c(year_1_list,f)
  }
  if(length(grep("_3y",f)) != 0){
    year_3_list <- c(year_3_list,f)
  }
}

imputed_psoriasis_data_full <- imputed_psoriasis_data_full %>%
  group_by(.imp) %>%
  mutate(
    ######### HEI 1 year ############
    # 1 year
    hei_score_1y = rowSums(across(year_1_list), 
                         na.rm = TRUE),
    ######### HEI 3 year ############
    # 3 year
    hei_score_3y = rowSums(across(year_3_list), 
                         na.rm = TRUE)
    
    )
```
get thirds
```{r}
get_thirds <- function(curr_vector){
  return(
    quantile(curr_vector, probs = c(0.333,0.667,1.0), na.rm = TRUE)
  )
}
```


divide hei score into thirds
```{r}
for (hei_year in c("hei_score_1y", "hei_score_3y")) {

  hei_year_t = paste(hei_year,"_thirds", sep = "")
  
  hei_year <- sym(hei_year)
  hei_year_t <- sym(hei_year_t)
  
  imputed_psoriasis_data_full <- imputed_psoriasis_data_full %>%
    group_by(.imp) %>%
    mutate( !!hei_year_t := case_when( 
      !!hei_year <= get_thirds(.data[[hei_year]])[[1]] ~ "low", 
      (!!hei_year > get_thirds(.data[[hei_year]])[[1]]) & (!!hei_year <= get_thirds(.data[[hei_year]])[[2]]) ~ "medium",
      (!!hei_year > get_thirds(.data[[hei_year]])[[2]]) & (!!hei_year <= get_thirds(.data[[hei_year]])[[3]]) ~ "high"
      )
    ) %>%
    mutate(!!hei_year_t := factor(.data[[hei_year_t]], levels = c("high","medium","low")))
}
```

convert back to mids object
```{r}
imputed_and_recoded_data <- imputed_psoriasis_data_full %>% 
  select(ABISnr,.imp,.id,
         hei_score_1y,hei_score_3y,
         hei_score_1y_thirds,hei_score_3y_thirds,Diagnos)

imputed_and_recoded_data <- as.mids(imputed_and_recoded_data)
```

glm on hei variable
```{r}
iter = 1
for (curr_var in c("hei_score_1y_thirds", "hei_score_3y_thirds")){
  models_complete <- with(imputed_and_recoded_data, 
                          glm(as.formula(paste("Diagnos ~",curr_var)), 
                              family = "binomial"))
  pool.fit <- pool(models_complete)

  if (iter == 1){
    imputed_regression_table_thirds <- summary(
      pool.fit, exponentiate = TRUE, conf.int = TRUE) %>%
      mutate_if(is.numeric, round,3) 
  } else {
    imputed_regression_table_thirds <- rbind(
      imputed_regression_table_thirds,
      summary(pool.fit, exponentiate = TRUE, conf.int = TRUE) %>%
        mutate_if(is.numeric, round,3))
  }
  iter = iter + 1

  }

iter = 1

for (curr_var in c("hei_score_1y", "hei_score_3y")){
  models_complete <- with(imputed_and_recoded_data, 
                          glm(as.formula(paste("Diagnos ~",curr_var)), 
                              family = "binomial"))
  pool.fit <- pool(models_complete)
  if (iter == 1){
  imputed_regression_table <- summary(
    pool.fit, exponentiate = TRUE, conf.int = TRUE) %>%
    mutate_if(is.numeric, round,3) 
  } else {
  imputed_regression_table <- rbind(
    imputed_regression_table_thirds,
    summary(pool.fit, exponentiate = TRUE, conf.int = TRUE) %>%
      mutate_if(is.numeric, round,3))
  }
  iter = iter + 1
  
  }
```



```{r}
original_data <- complete(imputed_and_recoded_data, action = 0)

iter = 1

for (iv in c("hei_score_1y","hei_score_3y","hei_score_1y_thirds","hei_score_3y_thirds")){
  if (iv %in% c("hei_score_1y","hei_score_3y")){
    curr_counts <- data.frame(
      no = original_data %>% filter(Diagnos==0) %>% nrow(),
      yes = original_data %>% filter(Diagnos==1) %>% nrow()
      )
  } else {
    curr_counts <- original_data %>% tabyl(!!sym(iv), Diagnos)
    curr_counts <- data.frame(
      no = curr_counts[,2],
      yes = curr_counts[,3]
    )
  }
  
  fit <- glm(as.formula(paste("Diagnos ~ ", iv)), family = "binomial", data = original_data)
  if (iter == 1){
   original_data_regression_table <- cbind(
     curr_counts,fit %>% tidy(exponentiate = TRUE, conf.int = TRUE))
  } else {
    original_data_regression_table <- rbind(original_data_regression_table,
                                            cbind(
                                              curr_counts,fit %>% 
                                                tidy(exponentiate = TRUE,
                                                     conf.int = TRUE)
                                              )
                                            )
  }
  iter = iter + 1

}
```

```{r}
curr_os <- Sys.info()["sysname"][[1]]

if (curr_os == "Windows"){
  output_dir <- "C:\\Users\\debda22\\OneDrive - Linköpings universitet\\early_nutrition\\healthy_eating_index_tables"
} else {
  output_dir <- "/Users/debojyoti/OneDrive - Linköpings universitet/early_nutrition/without_auto_immune_disease/healthy_eating_index_tables"
}

dir.create(output_dir)
```


save all the output tables
```{r}
dataframes2save <- to_vec(for (t in names(which(unlist(eapply(.GlobalEnv,is.data.frame))))) if(grepl("_regression_table",t)) t)
for (idf in seq_along(dataframes2save)) {
    filename <-paste(output_dir, paste(dataframes2save[[idf]], ".xlsx", collapse = ""), sep = "/")
    curr_dataframe2save <- get(dataframes2save[[1]])
    print(paste("saving ...",dataframes2save[[idf]]))
    writexl::write_xlsx(curr_dataframe2save, path = filename)
} 
```
